Multiple Dice Working as One: CAD Flows and Routing Architectures for Silicon Interposer FPGAs

### 2015-03-08 doc/journal/fpgapaperfinal/FPGAPaper/fpga2014paper.tex
Final revisions by Ehsan based on Google reviewers' comments
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4592 8e3573b8-cf2c-4f14-ef6d-137439e28b8b

where $N_{crossed}(i,j)$ is the number of times this path has to cross the interposer to go from $(x_i,y_i)$ to $(x_j,y_j)$ and $delay\_increase$ is the timing penalty of crossing the interposer.

@@

Clearly using bidirectional interposer wires with fanin transfer and fanout transfer is very beneficial, so we use these parameters in all future experiments. Adding additional fanin beyond transferring the fanin of cut wires is only a small further benefit so we use additional fanin=0 in subsequent sections. Adding these additional multiplexers will have a very small impact on die size as 10,000 muxes per cut would be typical in a large FPGA~\cite{xilinx7series} which is a very small fraction of the several million routing multiplexers in a large FPGA die.

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=\linewidth]{minChW_2.eps}
\caption{Minimum channel width vs. \textit{\% wires cut} for 2 dice and $1ns$ of \textit{delay increase}.}
\label{fig:standard_minW}
\end{figure}

>>>>

where $N_{crossed}(i,j)$ is the minimum number of times this path has to cross the interposer to go from $(x_i,y_i)$ to $(x_j,y_j)$ and $delay\_increase$ is the timing penalty of crossing the interposer.

@@

Clearly using bidirectional interposer wires with fanin transfer and fanout transfer is very beneficial, so we use these parameters in all future experiments. Adding additional fanin beyond transferring the fanin of cut wires is only a small further benefit so we use additional fanin=0 in subsequent sections. Adding these additional multiplexers and making the interposer drivers tri-statable causes less than a 0.1\% die area increase as 10,000 muxes per cut would be typical in a large FPGA~\cite{xilinx7series} which is a very small fraction of the several million routing multiplexers in a large FPGA die.

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=\linewidth]{MinChW_3.eps}
\caption{Minimum channel width vs. \textit{\% wires cut} for 2 dice and $1ns$ of \textit{delay increase}.}
\label{fig:standard_minW}
\end{figure}
